Recovery of deleted deep sequencing data sheds more light on the early Wuhan SARS-CoV-2 epidemic

### 2021-06-27 paper/paper.tex
update tables / figures with coverage after masking primer sites

\begin{table*}[b!]
{\small
\begin{tabular}{lrll}
\toprule
sample &  fraction sites called (21570-29550) &           patient group &                                        substitutions relative to proCoV2 \\
\midrule
A4 &                               0.9827 &        early outpatient &                                                                          none \\
C1 &                               0.9966 &        early outpatient &  G22081A (A=924, C=4, G=9), C28144T (C=6, T=1185), T29483G (C=1, G=45, T=1) \\
C2 &                               0.9962 &        early outpatient &                                                 C29095T (C=1, G=1, T=751)  \\
C9 &                               0.9536 &        early outpatient &                                  C28144T (C=3, T=823), G28514T (G=1, T=36)  \\
D9 &                               0.9585 &        early outpatient &                                                     C28144T (C=4, T=1653)  \\
D12 &                               0.9970 &        early outpatient &                                                     C28144T (C=8, T=2400)  \\
E1 &                               0.9759 &        early outpatient &                                                           C28144T (T=125)  \\
E5 &                               0.9758 &        early outpatient &              C24034T (A=5, C=3, T=74), T26729C (C=12), G28077C (C=142, G=4)  \\
E11 &                               0.9877 &        early outpatient &                                 C25460T (C=2, T=246), C28144T (C=1, T=412)  \\
F11 &                               0.9594 &        early outpatient &                             T25304A (A=9, T=1), C28144T (C=6, G=1, T=1328)  \\
G1 &                               0.9959 &        early outpatient &                                   none                                        \\
G11 &                               0.9677 &        early outpatient &                                  none                                         \\
H9 &                               0.9941 &        early outpatient &                                                     C28144T (C=2, T=1254)  \\
R11 &                               0.9987 &  hospital patient (Feb) &                               C21707T (T=401), C28144T (A=1, C=18, T=4265)  \\
\bottomrule
\end{tabular}
}
\caption{Samples for which the SARS-CoV-2 sequence could be called at $\ge$90\% of sites between 21,570 and 29,550, and the substitutions in this region relative to the putative SARS-CoV-2 progenitor proCoV2 inferred by \citet{kumar2021evolutionary}.
Numbers in parentheses after each substitution give the deep sequencing reads with each nucleotide identity.
\label{tab:mutations}
}
\end{table*}

@@

\begin{figure}[h!]
\centering
\includegraphics[width=\linewidth]{figures/coverage_all.pdf}
\caption{A version of Figure~\ref{fig:coverage} that shows coverage over the full length of the SARS-CoV-2 genome.
An interactive version of this plot is at \url{https://jbloom.github.io/SARS-CoV-2_PRJNA612766/coverage_all.html}.
}
\label{suppfig:coverage_all}
\end{figure}

>>>>

\begin{table*}[b!]
{\small
\begin{tabular}{lrll}
\toprule
sample &  fraction sites called (21570-29550) &           patient group &                                        substitutions relative to proCoV2 \\
\midrule
A4 &                               0.9266 &        early outpatient &                                                                          none \\
C1 &                               0.9396 &        early outpatient &  G22081A (A=924, C=4, G=9), C28144T (C=6, T=1185), T29483G (C=1, G=45, T=1) \\
C2 &                               0.9397 &        early outpatient &                                                 C29095T (C=1, G=1, T=751)  \\
C9 &                               0.9005 &        early outpatient &                                  C28144T (C=3, T=823), G28514T (G=1, T=36)  \\
D9 &                               0.9051 &        early outpatient &                                                     C28144T (C=4, T=1653)  \\
D12 &                               0.9400 &        early outpatient &                                                     C28144T (C=8, T=2400)  \\
E1 &                               0.9223 &        early outpatient &                                                           C28144T (T=125)  \\
E5 &                               0.9227 &        early outpatient &              C24034T (A=5, C=3, T=74), T26729C (C=12), G28077C (C=142, G=4)  \\
E11 &                               0.9321 &        early outpatient &                                 C25460T (C=2, T=246), C28144T (C=1, T=412)  \\
F11 &                               0.9054 &        early outpatient &                             T25304A (A=9, T=1), C28144T (C=6, G=1, T=1328)  \\
G1 &                               0.9396 &        early outpatient &                                   none                                        \\
G11 &                               0.9112 &        early outpatient &                                  none                                         \\
H9 &                               0.9381 &        early outpatient &                                                     C28144T (C=2, T=1254)  \\
R11 &                               0.9422 &  hospital patient (Feb) &                               C21707T (T=401), C28144T (A=1, C=18, T=4265)  \\
\bottomrule
\end{tabular}
}
\caption{Samples for which the SARS-CoV-2 sequence could be called at $\ge$90\% of sites between 21,570 and 29,550, and the substitutions in this region relative to the putative SARS-CoV-2 progenitor proCoV2 inferred by \citet{kumar2021evolutionary}.
Numbers in parentheses after each substitution give the deep sequencing reads with each nucleotide identity.
\label{tab:mutations}
}
\end{table*}

@@

\begin{figure}[h!]
\centering
\includegraphics[width=\linewidth]{figures/coverage_all.pdf}
\caption{A version of Figure~\ref{suppfig:coverage} that shows coverage over the full length of the SARS-CoV-2 genome.
An interactive version of this plot is at \url{https://jbloom.github.io/SARS-CoV-2_PRJNA612766/coverage_all.html}.
}
\label{suppfig:coverage_all}
\end{figure}
